Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-19 paper/intro.tex
tidied up

\subsubsection*{Contributions}
Our approach currently applies to common cyber-vulnerabilities, such
as overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service are not yet dealt with in our work.  Here, we do not
report on the invention of a new type of high-assurance component in
terms of capability; instead, our contribution is in the automated
synthesis of security-improving components from formal specifications
and a means to show that the synthesis is correct. We see the
following as the contributions of this paper:

\begin{compactitem}
  \item The language and semantics of code contracts to specify the behavior of high assurance components.
  \item Test contracts as a stylized mechanism to unit test code contracts inside the \brfcs\ framework with \agr.
  \item A synthesis path from code contracts to \ckml\ with a formal framework to argue correctness.
  \item A formal argument that \agr\ verification of code contracts carry over to the resulting binaries from the \ckml\ compiler.
  \item A case study that uses \brfcs\ to add cyber-resiliency to a non-trivial UAV system.
\end{compactitem}

The rest of the paper is organized as follows.
\secref{sec:overview} is an overview of the {\brfcs} environment.
Our approach is illustrated by a simple example in
\secref{sec:example}. Essential background on {\agr} verification and specification are
presented in \secref{sec:agree}.  The language and semantics of code
contracts are defined in \secref{sec:code-contracts}, and test
contracts are described in \secref{sec:testing}.  The synthesis pathway
is covered in Section~\ref{sec:synthesis}.
\secref{sec:case-study} discusses the case study.
This is followed by related work in \secref{sec:related-work}.
The conclusions and future work are in \secref{sec:conclusion}.

>>>>

\subsubsection*{Contributions and limitations}

Our work is embedded in a substantial collection of tools, so it is
important to clarify the research contribution. We see the following
as the contributions of this paper:

\begin{compactitem}
  \item The language and semantics of \emph{code contracts} provide a means
  to join system-level contract analysis results (arising from model
  checking) with component implementation correctness results (arising
  from property-preserving code generation).

\item \emph{Test contracts} as a
  stylized mechanism to unit test code contracts inside the \brfcs\
  framework with \agr.

\item A synthesis path from code contracts to \ckml, supported by a formal
   framework to argue correctness.

\item A formal argument that \agr\ verification of code contracts carry over
  to the resulting binaries from the \ckml\ compiler.

\item A case
  study that uses \brfcs\ to add cyber-resiliency to a non-trivial UAV
  system.
\end{compactitem}

Our approach currently applies to common cyber-vulnerabilities, such
as buffer overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service have not yet been addressed. Moreover, this work
does not introduce a new type of high-assurance component in terms of
capability; instead, our contribution is in the automated synthesis of
security-improving components from formal cyber-resilience
specifications and a means to show that the synthesis is correct. We
have not yet tried to apply {\brfcs} to problems outside the realm of
cyber-resilience; however, the notions of code and test contracts,
along with the system analysis and verified code generation facilities
promise to be useful in a wide variety of settings.

\subsubsection*{Organization}
The rest of the paper is organized as follows.
\secref{sec:overview} is an overview of the {\brfcs} environment.
Our approach is illustrated by a simple example in
\secref{sec:example}. Essential background on {\agr} verification and specification are
presented in \secref{sec:agree}.  The language and semantics of code
contracts are defined in \secref{sec:code-contracts}, and test
contracts are described in \secref{sec:testing}.  The synthesis pathway
is covered in Section~\ref{sec:synthesis}.
\secref{sec:case-study} discusses the case study.
This is followed by related work in \secref{sec:related-work}.
The conclusions and future work are in \secref{sec:conclusion}.
